ManyTypes4Py: A Benchmark Python Dataset for Machine Learning-based Type Inference\\

### 2021-03-01 paper/main.tex
Address MSR'21 reviewers' comments for the camera-ready version

\title{ManyTypes4Py: A benchmark Python dataset for machine learning-based type inference\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

We believe that there is a need for a large benchmark dataset that facilitates training ML-based type inference models, especially for Python. Unlike TypeScript's compiler, the Python interpreter cannot infer the type of variables or function signatures. Motivated by this, we present the ManyTypes4Py dataset, a large dataset to train ML models for predicting type annotations in Python. Currently, we are working on the Type4Py model \cite{mir2021type4py}, which is trained on the earlier version of the ManyTypes4Py dataset. The experimental results show that the model trained on our dataset is overall more accurate when compared to the same model trained on a smaller dataset \cite{mir2021type4py}.

@@

\begin{table*}[!t]
	\centering
	\label{tab:char-dataset}
	\caption{Characteristics of the ManyTypes4Py Dataset}
	\begin{threeparttable}
		\begin{tabular}{l c c c c}
			\toprule
			Metrics & \multicolumn{4}{@{} c @{}}{Dataset}  \\
			\cmidrule{2-5}
			& All & Training & Validation & Test \\
			\midrule
			Repositories & 5,382 & 4,913 & 2,789 & 3,796 \\
			Lines of code\tnote{a} & 22M & - & - & - \\
			\midrule
			Files & 183,916  & 132,409 & 14,675 & 36,832 \\
			...with type annotations & 50,838 (27.6\%) & 36,542 & 4,105  & 10,191  \\
			\midrule
			Functions & 2,096,797 & 1,509,048 & 169,519 & 418,230 \\
			...with comment & 1,129,573 (53.8\%) & 812,632 & 91,325 & 225,616 \\
			...with return type annotations & 325,532 (15.5\%) & 234,319 & 26,104 & 65,109 \\
			\midrule
			Arguments & 3,923,667 & 2,822,699 & 310,685 & 790,283 \\
			...with comment & 220,976 (5.6\%) & 159,453 & 16,924 & 44,599 \\ 
			...with type annotations & 480,793 (12.2\%) & 347,898 & 37,148 & 95,747 \\
			\midrule
			Types & 869,825 & 347,898 & 89,334 & 192,102 \\
			...unique & 67,060 & 53,614 & 13,995 & 23,572 \\
			\bottomrule
		\end{tabular}
		\begin{tablenotes}
			\item[a] {\footnotesize Comments and blank lines are ignored when counting lines of code.}
		\end{tablenotes}
	\end{threeparttable}
\end{table*}

@@

%\section*{Acknowledgment}
%This research work was funded by H2020 grant 825328 (FASTEN).

>>>>

\title{ManyTypes4Py: A Benchmark Python Dataset for Machine Learning-based Type Inference\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

We believe that there is a need for a large benchmark dataset that facilitates training ML-based type inference models, especially for Python. Unlike TypeScript's compiler, the Python interpreter cannot infer the type of variables or function signatures at compile time \cite{scott16}. Motivated by this, we present the ManyTypes4Py dataset, a large dataset to train ML models for predicting type annotations in Python. Currently, we are working on the Type4Py model \cite{mir2021type4py}, which is trained on the earlier version of the ManyTypes4Py dataset. The experimental results show that the model trained on our dataset is overall more accurate when compared to the same model trained on a smaller dataset \cite{mir2021type4py}.

@@

\begin{table*}[!t]
	\centering
	\label{tab:char-dataset}
	\caption{Characteristics of the ManyTypes4Py Dataset}
	\begin{threeparttable}
		\begin{tabular}{l c c c c}
			\toprule
			Metrics & \multicolumn{4}{@{} c @{}}{Dataset}  \\
			\cmidrule{2-5}
			& All & Training & Validation & Test \\
			\midrule
			Repositories\tnote{a} & 5,382 & 4,913 & 2,789 & 3,796 \\
			Lines of code\tnote{b} & 22M & - & - & - \\
			\midrule
			Files & 183,916  & 132,409 & 14,675 & 36,832 \\
			...with type annotations & 50,838 (27.6\%) & 36,542 & 4,105  & 10,191  \\
			\midrule
			Functions & 2,096,797 & 1,509,048 & 169,519 & 418,230 \\
			...with comment & 1,129,573 (53.8\%) & 812,632 & 91,325 & 225,616 \\
			...with return type annotations & 325,532 (15.5\%) & 234,319 & 26,104 & 65,109 \\
			\midrule
			Arguments & 3,923,667 & 2,822,699 & 310,685 & 790,283 \\
			...with comment & 220,976 (5.6\%) & 159,453 & 16,924 & 44,599 \\ 
			...with type annotations & 480,793 (12.2\%) & 347,898 & 37,148 & 95,747 \\
			\midrule
			Types & 869,825 & 347,898 & 89,334 & 192,102 \\
			...unique & 67,060 & 53,614 & 13,995 & 23,572 \\
			\bottomrule
		\end{tabular}
		\begin{tablenotes}
			\item[a] {\footnotesize Note that there is an intersection among repositories in the three sets as the dataset is split by files.}
			\item[b] {\footnotesize Comments and blank lines are ignored when counting lines of code.}
		\end{tablenotes}
	\end{threeparttable}
\end{table*}

@@

\section*{Acknowledgment}
This research work was funded by H2020 grant 825328 (FASTEN).
